IMPC Mouse data - Variance in sex differences

### 2019-11-06 scripts/2019_Nov1-FiguresRearranged_IMPC_variance_and_sex_difference.Rmd
Update Nov

```{r}
## Load raw data - save cleaned dataset as RDS for reuse
#data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
#    clean_raw_data()
#dir.create("export", F, F)
#saveRDS(data_raw, "export/data_clean.rds")
getwd()
data1 <- readRDS("export/data_clean.rds") 
#data1 
```

@@

## Meta analysis, Phase 1: across all traits
### Preparation
####Define population variable 
& add grouping variables

@@

compare

@@

#### Plot:  FIGURE 2 [Figure 4 in ms] (First-order meta analysis results)

@@

malebias_Fig2_alltraits <- 
ggplot(meta.plot2.all.e) +
  aes(x = GroupingTerm, y = percent, fill = sex) +
  geom_col() +
  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
  geom_text(data = subset(meta.plot2.all.e, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
	color = "white", size = 3.5) +
 facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
      scales= 'free', space='free') +
 scale_fill_brewer(palette = "Set2") +
theme_bw(base_size = 18) +
  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
        text = element_text(size=14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.position = "none",
        axis.title.x = element_blank(),
	  axis.title.y = element_blank()  ) +
	coord_flip()

#malebias_Fig2_alltraits

@@

malebias_Fig2_sigtraits <-  
ggplot(meta.plot2.sig.bothsexes.b) +
  aes(x = GroupingTerm, y = percent, fill = sex) +
  geom_col() +
  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
  geom_text(data = subset(meta.plot2.sig.bothsexes.b, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
	color = "white", size = 3.5) +
 facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
      scales= 'free', space='free') +
 scale_fill_brewer(palette = "Set2") +
theme_bw(base_size = 18) +
  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_blank(),
        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
        text = element_text(size=14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.position = "none",
        axis.title.x = element_blank(),
	  axis.title.y = element_blank()  ) +
	coord_flip()
```

@@

# *Plot Fig2 Sex difference in m/f ratio > 10%
malebias_Fig2_over10 <- 
ggplot(meta.plot2.over10.d) +
  aes(x = GroupingTerm, y = percent, fill = sex) +
  geom_col() +
  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
  geom_text(data = subset(meta.plot2.over10.d, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
	color = "white", size = 3.5) +
 facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
      scales= 'free', space='free') +
 scale_fill_brewer(palette = "Set2") +
theme_bw(base_size = 18) +
  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_blank(),
        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
        text = element_text(size=14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.position = "none",
        axis.title.x = element_blank(),
	  axis.title.y = element_blank()  ) +
	coord_flip()
# malebias_Fig2_over10

```
#### Create final combined Figure (Figure 2)
```{r}

Fig2 <- ggarrange(malebias_Fig2_alltraits, malebias_Fig2_sigtraits,malebias_Fig2_over10, nrow = 3, align = "v", heights = c(1.22,1,1), labels = c("A", "B", "C"))
Fig2
ggsave("CountDataCVR_RR_only.pdf", plot = Fig2, width = 6, height = 5) 
```

###  Overall results of second order meta analysis (Figure 4a)
#### Restructure data for plotting 
Data are restructured, and grouping terms are being re-ordered
```{r}
overall3 <- gather(overall2, parameter, value, c(lnCVR,  lnRR), factor_key= TRUE) #lnVR,

lnCVR.ci <- overall3 %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
#lnVR.ci <- overall3 %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
lnRR.ci <- overall3 %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)

@@

#### Plot FIGURE 4 (Second-order meta analysis results)
Preparation: Sub-Plot  for Figure 3: all traits
```{r}

@@

  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter), fill = 'black',
             color = 'black', size = 2.2, 
             show.legend = FALSE) +
  scale_x_continuous(limits=c(-0.24, 0.25), 
                     breaks = c(-0.2, -0.1, 0, 0.1, 0.2), 
                     name='Effect size') +
  geom_vline(xintercept=0, 
             color='black', 
             linetype='dashed')+
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_blank(),
	  axis.title.y = element_blank())

@@

#### Figure 4B- traits with CI not overlapping 0 
Prepare data 
create column with 1= different from zero, 0= zero included in CI
Male-biased (significant) traits
```{r}
meta.male.plot3.sig <- metacombo %>% 
    	mutate(sigCVR = ifelse(lnCVR_lower > 0, 1, 0),
	sigVR = ifelse(lnVR_lower > 0, 1, 0),
	sigRR = ifelse(lnRR_lower > 0, 1, 0))

@@

@@

Plot Fig3 all significant results (CI not overlapping zero) for males
```{r}

@@

#### Female Figure, significant traits
Female Fig3 sig

@@

#add missing GroupingTerms for plot POTENTIALLY DELETE
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Morphology")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Metabolism")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hematology")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hearing")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Eye")

#overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
#overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))

@@

Plot Fig3 all significant results (CI not overlapping zero, female )
```{r}

@@

#Metameta_Fig3_female.sig
```

#### Fig4 C >10%

@@

#### Male Fig 4 > 10% (male biased traits)
```{r}
meta.male.plot3.perc <- metacombo %>% 
    	mutate(percCVR = ifelse(lnCVR > log (11/10), 1, 0),			
	percVR = ifelse(lnVR > log (11/10), 1, 0),
	percRR = ifelse(lnRR > log (11/10), 1, 0))

@@

#overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b) 
overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.RR.perc.b)

@@

Plot Fig3 (4 in ms) all >10% difference (male bias)
```{r}

@@

# Metameta_Fig3_male.perc
```

####Female Fig 3 >10%
```{r}

@@

#overall.plot3.perc <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b) 
overall.plot3.perc <- full_join(plot3.meta.CVR.perc.b, plot3.meta.RR.perc.b)

@@

Plot Fig3 all >10% difference (female)
```{r}
Metameta_Fig3_female.perc <- overall4.perc %>% 
  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter),
             fill = 'salmon1', color = 'salmon1', size = 2.2, 
             show.legend = FALSE) +

@@

#Metameta_Fig3_female.perc

@@

#### Plot Fig4:  all plots combined
```{r}
library(ggpubr)
Fig3.bottom <- ggarrange(Metameta_Fig3_female.sig, Metameta_Fig3_male.sig, Metameta_Fig3_female.perc, Metameta_Fig3_male.perc, 
		   ncol = 2, nrow = 2, widths = c(1, 1.20), heights = c(1, 1))

Fig3 <- ggarrange(Metameta_Fig3_alltraits, Fig3.bottom, ncol = 1, nrow = 2, heights = c(1.4, 2.5))
Fig3
#ggsave("MetaResultsCVR_RR.pdf", plot = Fig3, width = 9, height = 6) 
```

@@

#### Exclude traits, merge datasets
```{r}
results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
nrow(results.allhetero.grouping2) #218
```

@@

metacombohetero$var.CVR

@@

heterog1

@@

###Plot FIGURE 4 (5 in ms) (Second-order meta analysis on heterogeneity)

Plot Fig4 all traits
```{r}

Metameta_Fig4_alltraits <- heterog4 %>%

  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter,
             fill = parameter, color = parameter), size = 2.2, 
             show.legend = FALSE) +
  scale_x_continuous(limits=c(-7.0, 1), 
                     #breaks = c(-2.0, -1.5, -1.0, -0.5, 0, 0.5, 1.0, 1.5, 2.0), 
                     name='Effect size') +
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_blank(),
	  axis.title.y = element_blank())

Metameta_Fig4_alltraits 
#ggsave("Fig4.pdf", plot = Metameta_Fig4_alltraits, width = 7, height = 6) 
```

>>>>

```{r}
## Load raw data - save cleaned dataset as RDS for reuse
#data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
#    clean_raw_data()
#dir.create("export", F, F)
#saveRDS(data_raw, "export/data_clean.rds")
#getwd()
data1 <- readRDS("export/data_clean.rds") 
#data1 
```

@@

## Meta analysis, Phase 1: across all traits
### Preparation
#### Define population variable 
& add grouping variables

@@

#compare

@@

#### Preparation for plots: Count data, based on First-order meta analysis results

@@

malebias_Fig2_alltraits <- 
ggplot(meta.plot2.all.e) +
  aes(x = GroupingTerm, y = percent, fill = sex) +
  geom_col() +
  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
  geom_text(data = subset(meta.plot2.all.e, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
	color = "white", size = 3.5) +
 facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
      scales= 'free', space='free') +
 scale_fill_brewer(palette = "Set2") +
theme_bw(base_size = 18) +
  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
        text = element_text(size=14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.position = "none",
        axis.title.x = element_blank() ,
	    axis.title.y =  element_blank()) +
	coord_flip()

#malebias_Fig2_alltraits     #(panel A in Figure 4 in ms)

@@

malebias_Fig2_sigtraits <-  
ggplot(meta.plot2.sig.bothsexes.b) +
  aes(x = GroupingTerm, y = percent, fill = sex) +
  geom_col() +
  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
  geom_text(data = subset(meta.plot2.sig.bothsexes.b, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
	color = "white", size = 3.5) +
 facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
      scales= 'free', space='free') +
 scale_fill_brewer(palette = "Set2") +
theme_bw(base_size = 18) +
  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
        text = element_text(size=14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.position = "none",
        axis.title.x = element_blank(),
	  axis.title.y = element_blank()  ) +
	coord_flip()
```

@@

# *Plot Fig2 Sex difference in m/f ratio > 10%
malebias_Fig2_over10 <- 
ggplot(meta.plot2.over10.d) +
  aes(x = GroupingTerm, y = percent, fill = sex) +
  geom_col() +
  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
  geom_text(data = subset(meta.plot2.over10.d, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
	color = "white", size = 3.5) +
 facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
      scales= 'free', space='free') +
 scale_fill_brewer(palette = "Set2") +
theme_bw(base_size = 18) +
  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_blank(),
        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
        text = element_text(size=14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.position = "none",
        axis.title.x = element_blank(),
	  axis.title.y = element_blank()  ) +
	coord_flip()

# malebias_Fig2_over10  (Panel C in Fig 5 in ms)

###  Overall results of second order meta analysis (Figure 4: overall, Figure 5: sex-bias)
#### Restructure data for plotting 
Data are restructured, and grouping terms are being re-ordered
```{r}
overall3 <- gather(overall2, parameter, value, c(lnCVR,  lnRR), factor_key= TRUE) #lnVR,

lnCVR.ci <- overall3 %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
lnVR.ci <- overall3 %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
lnRR.ci <- overall3 %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)

@@

#### Preparation for Plots FIGURE 4B & 5B, 5D (Second-order meta analysis results)
Preparation: Sub-Plot  for Figure 3: all traits (4B)
```{r}

@@

  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter), fill = 'black',
             color = 'black', size = 2.2, 
             show.legend = FALSE) +
  scale_x_continuous(limits=c(-0.24, 0.25), 
                     breaks = c(-0.2, -0.1, 0, 0.1, 0.2), 
                     name='Effect size') +
  geom_vline(xintercept=0, 
             color='black', 
             linetype='dashed')+
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_text(hjust = 0.5, size = 14),
	  axis.title.y = element_blank())

@@

#### Figure 5 - traits with CI not overlapping 0 
Prepare data 
create column with 1= different from zero, 0= zero included in CI
Male-biased (significant) traits
```{r}
meta.male.plot3.sig <- metacombo %>% 
    	mutate(sigCVR = ifelse(lnCVR_lower > 0, 1, 0),
	sigVR = ifelse(lnVR_lower > 0, 1, 0),
	sigRR = ifelse(lnRR_lower > 0, 1, 0))

@@

#str(overall.male.plot3)
```

@@

Plot Fig5b all significant results (CI not overlapping zero) for males
```{r}

@@

#### Female Figure, significant traits
Female Fig5B sig

@@

@@

Plot Fig5B all significant results (CI not overlapping zero, female )
```{r}

@@

#Metameta_Fig3_female.sig (Figure 5B left panel)
```

#### Fig5 D >10%

@@

#### Male Fig 5D > 10% (male biased traits)
```{r}
meta.male.plot3.perc <- metacombo %>% 
    	mutate(percCVR = ifelse(lnCVR > log (11/10), 1, 0),			
	percVR = ifelse(lnVR > log (11/10), 1, 0),
	percRR = ifelse(lnRR > log (11/10), 1, 0))

@@

plot3.male.meta.CVR.Vr.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b) 
overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.Vr.perc , plot3.male.meta.RR.perc.b)

@@

Plot Fig5D  all >10% difference (male bias)
```{r}

@@

# Metameta_Fig3_male.perc (Figure 5D right panel)
```

#### Female Fig 5D >10%
```{r}

@@

plot3.meta.CVR.perc.c <- full_join(plot3.meta.CVR.perc.b, plot3.meta.VR.perc.b) 
overall.plot3.perc <- full_join(plot3.meta.CVR.perc.c, plot3.meta.RR.perc.b)

@@

Plot Fig5D all >10% difference (female)
```{r}
Metameta_Fig3_female.perc <- overall4.perc %>% 
  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter),
             fill = 'salmon1', color = 'salmon1', size = 2.2, 
             show.legend = FALSE) +

@@

#Metameta_Fig3_female.perc (Figure 5D left panel)

@@

#### Plot Fig5:   plots combined
```{r}
library(ggpubr)
Fig5b <- ggarrange(Metameta_Fig3_female.sig, Metameta_Fig3_male.sig,  
		   ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1))

Fig5d <- ggarrange(Metameta_Fig3_female.perc, Metameta_Fig3_male.perc,  
		   ncol = 2, nrow = 1, widths = c(1, 1.20), heights = c(1, 1))

#end combination Figure 5

Fig5 <- ggarrange(malebias_Fig2_sigtraits,  malebias_Fig2_over10, Fig5b,Fig5d,  ncol = 1, nrow = 4, heights = c(2.3,2,2.1,2), labels = c("A", " ", "B", " "))
Fig5

@@

#### Exclude traits, merge datasets
```{r}
results.allhetero.grouping2 <- results.allhetero.grouping[results.allhetero.grouping$s.nlevels.strain.VR != 0, ]
#nrow(results.allhetero.grouping2) #218
```

@@

# Final fixed effects meta-analyses within grouping terms, with SE of the estimate

#metacombohetero$var.CVR

@@

@@

### Plot FIGURE 4 - C(Second-order meta analysis on heterogeneity)

Plot Fig4 all traits
```{r}
heterog5 <- heterog4
heterog5$mean <- as.numeric(exp(heterog5$value))
heterog5$ci.l <- as.numeric(exp(heterog5$ci.low))
heterog5$ci.h <- as.numeric(exp(heterog5$ci.high))

heterog6 <- heterog5

Hetero4c <- 
heterog6 %>% filter(
  parameter ==  "heteroCVR" | parameter ==  "heteroRR") %>% 
  ggplot(aes(y= GroupingTerm, x= mean)) +
  geom_errorbarh(aes(xmin = ci.l, 
                     xmax = ci.h), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter), fill = 'black',
             color = 'black', size = 2.2, 
             show.legend = FALSE) +
  scale_x_continuous(limits=c( -0.1, 1.4), 
                     #breaks = c(0, 0.1, 0.2), 
                     name='sigma^2') +
  #geom_vline(xintercept=0, 
             #color='black', 
             #linetype='dashed')+
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_text(hjust = 0.5, size = 14),
	  axis.title.y = element_blank())

#Hetero4c

#ggsave("Fig4.pdf", plot = Metameta_Fig4_alltraits, width = 7, height = 6) 
```

#### Combined Figure 4: overall (Count data, Meta anlysis results, Heterogeneity)
```{r}

Fig4 <- ggarrange(malebias_Fig2_alltraits, Metameta_Fig3_alltraits, Hetero4c, nrow = 3, align = "v", heights = c(1,1,1), labels = c("A", "B", "C"))
Fig4
#ggsave("Fig4_OverallResults.pdf", plot = Fig4, width = 6, height = 5) 
```

## Supplemental Figures
```{r}
## Heterogneity, S1 C

HeteroS1 <- heterog5 %>% 
  ggplot(aes(y= GroupingTerm, x= mean)) +
  geom_errorbarh(aes(xmin = ci.l, 
                     xmax = ci.h), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter), fill = 'black',
             color = 'black', size = 2.2, 
             show.legend = FALSE) +
  scale_x_continuous(limits=c( -0.1, 1.4), 
                     #breaks = c(0, 0.1, 0.2), 
                     name='Effect size') +
  #geom_vline(xintercept=0, 
             #color='black', 
             #linetype='dashed')+
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_blank(),
	  axis.title.y = element_blank())

#HeteroS1

#ggsave("Fig4.pdf", plot = Metameta_Fig4_alltraits, width = 7, height = 6) 
```
## Count data, including lnVR (Fig S1 A)
```{r}
# *Prepare data for all traits

meta.plot2.all.bS1 <- gather(meta.plot2.all, trait, value, c(lnCVR, lnVR,  lnRR))

meta.plot2.all.bS1$trait <- factor(meta.plot2.all.bS1$trait, levels =c("lnCVR","lnVR", "lnRR") )

meta.plot2.all.cS1 <- meta.plot2.all.bS1  %>%
				group_by_at(vars(trait, GroupingTerm)) %>%
				summarise(malebias = sum(value > 0), femalebias = sum(value<= 0), total= malebias + femalebias, 
					malepercent = malebias*100/total, femalepercent = femalebias*100/total)

meta.plot2.all.cS1$label <- "All traits"

meta.plot2.all.dS1 <- as.data.frame(meta.plot2.all.cS1)
meta.plot2.all.eS1 <- gather(meta.plot2.all.dS1, key = sex, value = percent, malepercent:femalepercent, factor_key = TRUE)

meta.plot2.all.eS1$samplesize <- with(meta.plot2.all.eS1, ifelse(sex == "malepercent", malebias, femalebias) )

malebias_FigS1_alltraits <- 
ggplot(meta.plot2.all.eS1) +
  aes(x = GroupingTerm, y = percent, fill = sex) +
  geom_col() +
  geom_hline(yintercept = 50, linetype = "dashed", color = "gray40") +
  geom_text(data = subset(meta.plot2.all.eS1, samplesize != 0), aes(label = samplesize), position = position_stack(vjust = .5), 
	color = "white", size = 3.5) +
 facet_grid(cols = vars(trait), rows = vars(label),  labeller = label_wrap_gen(width = 18), 
      scales= 'free', space='free') +
 scale_fill_brewer(palette = "Set2") +
theme_bw(base_size = 18) +
  	theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL,linetype = "blank", fill = "gray90"),
        text = element_text(size=14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.position = "none",
        axis.title.x = element_blank() ,
	    axis.title.y =  element_blank()) +
	coord_flip()

#malebias_FigS1_alltraits     #(panel A in Figure S1)
```
###  Overall results of second order meta analysis (Figure 4: overall, Figure 5: sex-bias), INCLUDING VR
#### Restructure data for plotting 
Restructure MALE data for plotting 
```{r}
overall3.male.sigS <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

lnCVR.ci <- overall3.male.sigS  %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
lnVR.ci <- overall3.male.sigS  %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
lnRR.ci <- overall3.male.sigS  %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)

overall4.male.sigS <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

overall4.male.sigS$label <- "CI not overlapping zero"

```
Data are restructured, and grouping terms are being re-ordered
```{r}
overall3S <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

lnCVR.ci <- overall3S %>% filter(parameter == "lnCVR") %>% mutate(ci.low = lnCVR_lower, ci.high = lnCVR_upper)
lnVR.ci <- overall3S %>% filter(parameter == "lnVR") %>% mutate(ci.low = lnVR_lower, ci.high = lnVR_upper)
lnRR.ci <- overall3S %>% filter(parameter == "lnRR") %>% mutate(ci.low = lnRR_lower, ci.high = lnRR_upper)

overall4S <- bind_rows(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
overall4S$GroupingTerm <- factor(overall4S$GroupingTerm, rev(levels(overall4S$GroupingTerm)))
overall4S$label <- "All traits"

#### Preparation for Plots FIGURE S1B & S2B, S2D (Second-order meta analysis results, INCL lnVR)
Preparation: Sub-Plot  for Figure S1: all traits (S1 B)
```{r}
Metameta_FigS1_alltraits <- overall4S %>%

  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter), fill = 'black',
             color = 'black', size = 2.2, 
             show.legend = FALSE) +
  scale_x_continuous(limits=c(-0.24, 0.25), 
                     breaks = c(-0.2, -0.1, 0, 0.1, 0.2), 
                     name='Effect size') +
  geom_vline(xintercept=0, 
             color='black', 
             linetype='dashed')+
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_text(hjust = 0.5, size = 14),
	  axis.title.y = element_blank())

#Metameta_FigS1_alltraits
